### 2024-06-16 Paper/appendix.tex

        \Huge
        Appendix \\
        \LARGE
        A Perfect Storm and the Importance of Favourable First-Nature Geography \\

@@

\FloatBarrier
\subsection{All occupational major categories estimates} 
\begin{table}[]
    \centering
    \caption{\label{tab:occ1} Effect on occupation in 1901 (HISCO first digit 1 to 3)}
    \footnotesize
    \begin{tabular}{ccccc}
\toprule
hisco & Affected & Approach & Estimate (1901) & n parishes\\
\midrule
0/1 & MA & 3: log(x+1) & -0.595 (0.332) & 1589\\
0/1 & MA & 4: asinh(x) & -0.566 (0.394) & 1589\\
0/1 & MA & 2: Intensive & -0.454 (0.441) & 1323\\
0/1 & MA & 1: Extensive & 0.434 (0.148) & 1589\\
0/1 & Dummy & 4: asinh(x) & -0.082 (0.063) & 1589\\
0/1 & Dummy & 3: log(x+1) & -0.08 (0.053) & 1589\\
0/1 & Dummy & 1: Extensive & 0.068 (0.027) & 1589\\
0/1 & Dummy & 2: Intensive & -0.048 (0.075) & 1323\\
2 & MA & 3: log(x+1) & -1.316 (0.447) & 1589\\
2 & MA & 4: asinh(x) & -1.116 (0.502) & 1589\\
2 & MA & 2: Intensive & -0.381 (0.754) & 672\\
2 & MA & 1: Extensive & 0.119 (0.156) & 1589\\
2 & Dummy & 3: log(x+1) & -0.111 (0.082) & 1589\\
2 & Dummy & 2: Intensive & 0.091 (0.151) & 672\\
2 & Dummy & 4: asinh(x) & -0.088 (0.092) & 1589\\
2 & Dummy & 1: Extensive & -0.024 (0.027) & 1589\\
3 & MA & 2: Intensive & 3.793 (2.151) & 51\\
3 & MA & 1: Extensive & 0.595 (0.271) & 1589\\
3 & Dummy & 2: Intensive & 0.501 (0.154) & 51\\
3 & Dummy & 1: Extensive & 0.139 (0.045) & 1589\\
3 & MA & 3: log(x+1) & -0.087 (0.377) & 1589\\
3 & MA & 4: asinh(x) & -0.083 (0.476) & 1589\\
3 & Dummy & 4: asinh(x) & 0.02 (0.078) & 1589\\
3 & Dummy & 3: log(x+1) & 0.017 (0.062) & 1589\\
\bottomrule
\end{tabular}
\parbox{0.9\textwidth}{
\caption*{\footnotesize \textit{Notes:} Parameter estimate of the effect on occupational structure of the channel in 1901. Each row corresponds to a sepperate regression with all individuals with hisco codes starting with 0/1, 2 or 3 as outcome. The last column shows the number of parishes included in the regression, which is different from the full sample (1589) in the intensive margin estimates. As a rule of thumb, results with fewer than 100 observations should be entirely disregarded. *** $p< 0.01$ ** $p< 0.05$ * $p< 0.10$. Standard errors clustered on the parish level in parenthesis. All p-values are Bonferroni-corrected. \\ \textit{Source:} Danish census data.}
}
\end{table}

\begin{table}[]
    \centering
    \caption{\label{tab:occ2} Effect on occupation in 1901 (HISCO first digit 4 to 9)}
    \footnotesize
    \begin{tabular}{ccccc}
\toprule
hisco & Affected & Approach & Estimate (1901) & n parishes\\
\midrule
4 & MA & 2: Intensive & -5.025 (3.974) & 24\\
4 & MA & 4: asinh(x) & -2.055** (0.56) & 1589\\
4 & MA & 3: log(x+1) & -1.707** (0.47) & 1589\\
4 & Dummy & 2: Intensive & -0.306 (0.627) & 24\\
4 & MA & 1: Extensive & -0.299 (0.196) & 1589\\
4 & Dummy & 4: asinh(x) & -0.28 (0.1) & 1589\\
4 & Dummy & 3: log(x+1) & -0.223 (0.084) & 1589\\
4 & Dummy & 1: Extensive & -0.101 (0.035) & 1589\\
5 & MA & 2: Intensive & 1.073 (0.974) & 566\\
5 & MA & 1: Extensive & -0.829*** (0.183) & 1589\\
5 & MA & 4: asinh(x) & -0.744 (0.561) & 1589\\
5 & MA & 3: log(x+1) & -0.427 (0.461) & 1589\\
5 & Dummy & 2: Intensive & 0.286 (0.171) & 566\\
5 & Dummy & 1: Extensive & -0.055 (0.031) & 1589\\
5 & Dummy & 3: log(x+1) & 0.037 (0.077) & 1589\\
5 & Dummy & 4: asinh(x) & 0.016 (0.094) & 1589\\
6 & MA & 2: Intensive & 1.714*** (0.172) & 1544\\
6 & MA & 3: log(x+1) & 0.512 (0.288) & 1589\\
6 & MA & 4: asinh(x) & 0.363 (0.317) & 1589\\
6 & Dummy & 2: Intensive & 0.254*** (0.029) & 1544\\
6 & MA & 1: Extensive & -0.246*** (0.049) & 1589\\
6 & Dummy & 3: log(x+1) & 0.136*** (0.035) & 1589\\
6 & Dummy & 4: asinh(x) & 0.122* (0.037) & 1589\\
6 & Dummy & 1: Extensive & -0.025*** (0.004) & 1589\\
7/8/9 & MA & 2: Intensive & 1.609*** (0.332) & 1524\\
7/8/9 & MA & 4: asinh(x) & 0.654 (0.383) & 1589\\
7/8/9 & MA & 3: log(x+1) & 0.53 (0.349) & 1589\\
7/8/9 & MA & 1: Extensive & -0.227*** (0.051) & 1589\\
7/8/9 & Dummy & 2: Intensive & 0.181 (0.062) & 1524\\
7/8/9 & Dummy & 4: asinh(x) & 0.095 (0.066) & 1589\\
7/8/9 & Dummy & 3: log(x+1) & 0.08 (0.061) & 1589\\
7/8/9 & Dummy & 1: Extensive & -0.02 (0.007) & 1589\\
\bottomrule
\end{tabular}
\parbox{0.9\textwidth}{
\caption*{\footnotesize \textit{Notes:} Parameter estimate of the effect on occupational structure of the channel in 1901. Each row corresponds to a sepperate regression with all individuals with hisco codes starting with 4, 5, or 6/8/9 as outcome. The last column shows the number of parishes included in the regression, which is different from the full sample (1589) in the intensive margin estimates. As a rule of thumb, results with fewer than 100 observations should be entirely disregarded. *** $p< 0.01$ ** $p< 0.05$ * $p< 0.10$. Standard errors clustered on the parish level in parenthesis. All p-values are Bonferroni-corrected. \\ \textit{Source:} Danish census data.}
}
\end{table}

>>>>

        \Huge
        Appendix \\
        \LARGE
        A Perfect Storm: First-Nature Geography and Economic Development \\

@@

\FloatBarrier
\subsection{All occupational major categories estimates} 
\begin{table}[]
    \centering
    \caption{\label{tab:occ1} Effect on occupation in 1901 (HISCO first digit 1 to 3)}
    \footnotesize
    \begin{tabular}{ccccc}
\toprule
hisco & Affected & Approach & Estimate (1901) & n parishes\\
\midrule
0/1 & MA & 3: log(x+1) & -0.642 (0.337) & 1589\\
0/1 & MA & 4: asinh(x) & -0.595 (0.397) & 1589\\
0/1 & MA & 1: Extensive & 0.414 (0.139) & 1589\\
0/1 & MA & 2: Intensive & -0.41 (0.445) & 1342\\
0/1 & Dummy & 3: log(x+1) & -0.083 (0.06) & 1589\\
0/1 & Dummy & 4: asinh(x) & -0.081 (0.07) & 1589\\
0/1 & Dummy & 1: Extensive & 0.064 (0.025) & 1589\\
0/1 & Dummy & 2: Intensive & -0.047 (0.079) & 1342\\
2 & MA & 3: log(x+1) & -0.871 (0.463) & 1589\\
2 & MA & 4: asinh(x) & -0.561 (0.521) & 1589\\
2 & MA & 1: Extensive & 0.182 (0.148) & 1589\\
2 & Dummy & 3: log(x+1) & -0.085 (0.085) & 1589\\
2 & Dummy & 2: Intensive & 0.081 (0.148) & 764\\
2 & Dummy & 4: asinh(x) & -0.056 (0.096) & 1589\\
2 & MA & 2: Intensive & 0.04 (0.761) & 764\\
2 & Dummy & 1: Extensive & -0.015 (0.025) & 1589\\
3 & MA & 2: Intensive & 1.962 (4.096) & 75\\
3 & Dummy & 2: Intensive & 1.252 (0.472) & 75\\
3 & MA & 1: Extensive & 1.128*** (0.259) & 1589\\
3 & MA & 4: asinh(x) & 0.697 (0.479) & 1589\\
3 & MA & 3: log(x+1) & 0.486 (0.381) & 1589\\
3 & Dummy & 1: Extensive & 0.169*** (0.044) & 1589\\
3 & Dummy & 4: asinh(x) & 0.101 (0.087) & 1589\\
3 & Dummy & 3: log(x+1) & 0.073 (0.07) & 1589\\
\bottomrule
\end{tabular}
\parbox{0.9\textwidth}{
\caption*{\footnotesize \textit{Notes:} Parameter estimate of the effect on occupational structure of the channel in 1901. Each row corresponds to a sepperate regression with all individuals with hisco codes starting with 0/1, 2 or 3 as outcome. The last column shows the number of parishes included in the regression, which is different from the full sample (1589) in the intensive margin estimates. As a rule of thumb, results with fewer than 100 observations should be entirely disregarded. *** $p< 0.01$ ** $p< 0.05$ * $p< 0.10$. Standard errors clustered on the parish level in parenthesis. All p-values are Bonferroni-corrected. \\ \textit{Source:} Danish census data.}
}
\end{table}

\begin{table}[]
    \centering
    \caption{\label{tab:occ2} Effect on occupation in 1901 (HISCO first digit 4 to 9)}
    \footnotesize
    \begin{tabular}{ccccc}
\toprule
hisco & Affected & Approach & Estimate (1901) & n parishes\\
\midrule
4 & MA & 2: Intensive & -4.772 (3.826) & 28\\
4 & MA & 4: asinh(x) & -1.342 (0.576) & 1589\\
4 & MA & 3: log(x+1) & -1.121 (0.489) & 1589\\
4 & Dummy & 2: Intensive & -0.353 (0.402) & 28\\
4 & Dummy & 4: asinh(x) & -0.182 (0.103) & 1589\\
4 & Dummy & 3: log(x+1) & -0.143 (0.087) & 1589\\
4 & MA & 1: Extensive & -0.123 (0.202) & 1589\\
4 & Dummy & 1: Extensive & -0.058 (0.036) & 1589\\
5 & MA & 4: asinh(x) & -0.943 (0.554) & 1589\\
5 & MA & 1: Extensive & -0.662*** (0.163) & 1589\\
5 & MA & 3: log(x+1) & -0.625 (0.462) & 1589\\
5 & Dummy & 2: Intensive & 0.309 (0.159) & 660\\
5 & MA & 2: Intensive & 0.302 (0.881) & 660\\
5 & Dummy & 3: log(x+1) & 0.057 (0.079) & 1589\\
5 & Dummy & 4: asinh(x) & 0.042 (0.094) & 1589\\
5 & Dummy & 1: Extensive & -0.031 (0.028) & 1589\\
6 & MA & 2: Intensive & 1.173*** (0.196) & 1545\\
6 & MA & 1: Extensive & -0.243*** (0.049) & 1589\\
6 & Dummy & 2: Intensive & 0.197*** (0.031) & 1545\\
6 & MA & 4: asinh(x) & -0.123 (0.322) & 1589\\
6 & Dummy & 3: log(x+1) & 0.085 (0.036) & 1589\\
6 & Dummy & 4: asinh(x) & 0.072 (0.038) & 1589\\
6 & MA & 3: log(x+1) & 0.025 (0.294) & 1589\\
6 & Dummy & 1: Extensive & -0.024*** (0.004) & 1589\\
7/8/9 & MA & 2: Intensive & 1.763*** (0.339) & 1530\\
7/8/9 & MA & 4: asinh(x) & 0.813 (0.39) & 1589\\
7/8/9 & MA & 3: log(x+1) & 0.709 (0.358) & 1589\\
7/8/9 & MA & 1: Extensive & -0.218*** (0.05) & 1589\\
7/8/9 & Dummy & 2: Intensive & 0.215** (0.063) & 1530\\
7/8/9 & Dummy & 4: asinh(x) & 0.123 (0.068) & 1589\\
7/8/9 & Dummy & 3: log(x+1) & 0.11 (0.063) & 1589\\
7/8/9 & Dummy & 1: Extensive & -0.02 (0.007) & 1589\\
\bottomrule
\end{tabular}
\parbox{0.9\textwidth}{
\caption*{\footnotesize \textit{Notes:} Parameter estimate of the effect on occupational structure of the channel in 1901. Each row corresponds to a sepperate regression with all individuals with hisco codes starting with 4, 5, or 6/8/9 as outcome. The last column shows the number of parishes included in the regression, which is different from the full sample (1589) in the intensive margin estimates. As a rule of thumb, results with fewer than 100 observations should be entirely disregarded. *** $p< 0.01$ ** $p< 0.05$ * $p< 0.10$. Standard errors clustered on the parish level in parenthesis. All p-values are Bonferroni-corrected. \\ \textit{Source:} Danish census data.}
}
\end{table}
